Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-08-13 Manuscript.Rmd
check for more sequential effects (completion n) and new supplemental plot

# get the number of continuous quits before current trial
seqQuits <- function(subjData = 1){

    # get the lag
    tempSeq <- sequence(rle(subjData)$lengths) # sequence
    tempSeq[subjData==1] <- 0 # not interested in completed runs, just quits
    tempSeq <- c(0,tempSeq) # lag it so it can be used as a t-1 regressor

@@

@@

>>>>

# get the number of continuous quits before current trial
seqQuits <- function(subjData = 1, event = 1){
    # event dictates whether to only look at quits (1) or completions (0)
    # basically, add the event that won't be considered in the sequential tally regressor

    # get the lag
    tempSeq <- sequence(rle(subjData)$lengths) # sequence
    tempSeq[subjData == event] <- 0 # not interested in completed runs, just quits
    tempSeq <- c(0, tempSeq) # lag it so it can be used as a t-1 regressor

@@

## potential for reviewers
# ## track the number of completions
# # the idea here is that if participants are fatigued by recent physical exertion, they should seek breaks as a function of continuous work
# # the results is no. In fact, the more they recently completed, the more likely they were to accept
# # this was true even when just testing the physical group
# new <- lapply(seq(2, 7), function(tail) {
#   dat <- dataBtw %>%
#     filter(Cost == "Physical") %>%
#     group_by(SubjID) %>%
#     mutate(recentTravels = seqQuits(Completed),
#            recentCompletions = seqQuits(Completed, 0),
#            recentOffers = ifelse(TrialN < (tail + 1), Offer, Reduce(`+`, shift(Offer, 1:tail)))) 
#   
#   glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + recentCompletions + (1 | SubjID), data = dat, family = "binomial")
# })
# 
# # then get the summary of the tail length that reduced the AIC the most
# historyIndex_btw <- which(sapply(new, function(iter) {AIC(iter)}) == min(sapply(new, function(iter) {AIC(iter)})))
# 
# round(summary(new[[historyIndex_btw]])$coefficients, digits = 2)

@@

## alternative form of the plot, instead showing a decay of acceptances as a function of handling time
# more of a traditional discounting plot
# dataBtw %>%
#   filter(Choice < 2) %>% # , Cost != "Easy"
#   group_by(SubjID, Cost, Handling, Offer, optimal) %>%
#   summarise(pAccept = mean(Choice), .groups = 'drop') %>%
#   group_by(Cost, Handling, Offer, optimal) %>%
#   summarise(meanComplete = mean(pAccept),
#             SE = sd(pAccept) / sqrt(length(pAccept)), .groups = 'drop') %>%
#   mutate(Handling = factor(Handling, levels = c(2, 10, 14)),
#          Offer = factor(Offer, levels = c(4, 8, 20))) %>%
#   ggplot(aes(Offer, meanComplete, group = interaction(Cost, Handling), color = Cost)) +
#     geom_point(size = 2) +
#     scale_color_manual(values = colsBtw) +
#     geom_line(aes(linetype = Handling), size = 0.7) +
#     geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.1, size = 0.5) +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 12))
